---
title: "Activity: Nuclear Reactors"
author: "Mysha Nihal"
output: html_notebook
---

```{r}
library(tidyverse)

```

## Scrape the Data 

```{r}
#My code here....

library("rvest")

webpage <- "https://en.wikipedia.org/wiki/List_of_commercial_nuclear_reactors"

table_list <- webpage %>%
  read_html(header = TRUE) %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)

```


## Your turn: In what ways is the table tidy? How is it not tidy? What’s different about it from a tidy table?

- The table has some single columns with single variables which makes it somewhat like tidy but the table is not tidy. 

- Each variable should have its own column. The table has multiple variables but they are not separate columns for each of them.

- The webpage contains multiple tables.


## Your Turn: Plot Net Generation Capacity vs Construction Date

```{r}

library(ggplot2)

table <- table_list[[10]] #random table chosen

table$`Capacity(MW)` <- as.numeric(gsub("[^0-9.]", "", table$`Capacity(MW)`))

table$Beginbuilding <- as.Date(table$Beginbuilding, format = "%d %b %Y")

table <- table[complete.cases(table[c("Capacity(MW)", "Beginbuilding")]), ]

# Plot the data
ggplot(table, aes(x = Beginbuilding, y = `Capacity(MW)`)) +
  geom_point(shape = 15, size = .5) +
  labs(x = "Construction Date", y = "Net Generation Capacity")

```


## Your Turn: Scrape & Clean China Data (then merge with Japan)

```{r}

china <- table_list[[10]]

china <- china[, c("Plantname", "UnitNo.", "Type", "Model", "Capacity(MW)", "Beginbuilding", "Commercialoperation")]

japan <- table_list[[21]]

japan <- japan[, c("Plantname", "UnitNo.", "Type", "Model", "Capacity(MW)", "Beginbuilding", "Commercialoperation")]

merged <- rbind(china, japan)

show(merged)

```



## Your Turn: Reconstruct Info Graphic of Japan Reactors (or other country of interest)


```{r}

library(ggplot2)
library(dplyr)
library(lubridate)

japan <- table_list[[21]]
japan <- japan[, c("Plantname", "UnitNo.", "Type", "Model", "Capacity(MW)", "Beginbuilding", "Commercialoperation", "Status")]

japan$Beginbuilding <- dmy(japan$Beginbuilding)
japan$Commercialoperation <- dmy(japan$Commercialoperation)

japan <- japan %>%
  filter(!is.na(Beginbuilding) & !is.na(Commercialoperation))

japan <- japan %>%
  mutate(Duration = Commercialoperation - Beginbuilding)

japan <- japan %>%
  mutate(ReactorID = paste(Plantname, UnitNo., sep = " "))

# Select a subset of reactors to display
num_reactors <- 25
selected_reactors <- sample(unique(japan$ReactorID), num_reactors)

japan <- japan %>%
  filter(ReactorID %in% selected_reactors)

ggplot(japan, aes(x = Commercialoperation, xend = Beginbuilding, y = ReactorID, yend = ReactorID, color = Type, shape = Status)) +
  geom_segment(size = 1) +
  geom_point(size = 2) +
  labs(x = "Operation Year", y = "Reactor ID", title = "Duration from Construction to Operation") +
  scale_x_date(date_labels = "%Y", date_breaks = "5 years") +
  scale_shape_manual(values = c("Inoperable" = 2, "Shut down" = 3, "Operational" = 16)) +
  theme_minimal() +
  theme(axis.text.y = element_text(hjust = 0, vjust = 0.2))

```

